\documentclass[10pt,letterpaper]{article}

% ATS Compatibility:
\input{glyphtounicode}
\pdfgentounicode=1

\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage[usenames, dvipsnames]{color}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor={black},
}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\renewcommand{\baselinestretch}{1.025}

\subsectionfont{\fontsize{11}{15}\selectfont}


\newcommand{\items}[2]
{
	% @ is a column separator 
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} r}
		#1 & #2 \\
	\end{tabular*}
}


\newcommand{\header}[2]
{
	% @ is a column separator 
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} r}
		\hspace{-27pt} #1 & #2 \\
	\end{tabular*}
}

\newcommand{\sectionbreak}
{
	\vspace{-1.2em}
	\rule{\textwidth}{1.7pt}
	\vspace{-1.7em}
}

\newcommand{\twocol}[2]
{
	\begin{tabular*}{\linewidth}{l @{\hspace{108.5pt}} l}
		 #1 & #2 \\
	\end{tabular*}
	\vspace{-15pt}

}

\begin{document}

\begin{center}
{\LARGE \textbf{Aashir Farooqi}}

\vspace{0.5em}
\ (949)-226-9612 \textbar 
\ afarooqi@ucdavis.edu\textbar
\ \href{https://github.com/AashPointO}{\emph{\underline{\smash{https://github.com/AashPointO}}}}
\\
\end{center}
\vspace{-20pt}


\subsection*{Education}
\sectionbreak

\begin{itemize}

\item[] 
	\header
		{\textbf{University of California, Davis}}
		{\textbf{Fall 2016 - Summer 2020}}
\item[]
	\vspace{-2.5pt}
	\items
		{\textbf{Major:} Computer Engineering, B.S}
		{}
	\items
		{\textbf{GPA:} 3.4}
		{}
	\items
		{\textbf{CS Coursework:} Algorithm Design \& Analysis, Applied Linear Algebra, Operating Systems, Networks.}
		{}
	\items
		{\textbf{EE Coursework:} Embedded Systems, Digital Systems, Circuits, Signal Processing.}
		{}
{\vspace{-0.6em}}
	
\end{itemize}

\vspace{-24.65pt}

\subsection*{Experience}
\sectionbreak

\begin{itemize}
	\item[]
		\header
			{\textbf{Firmware \& Hardware Engineer - Research Assistant}} 
			{\textbf{April 2018 - June 2020}}
		\header
		{\textbf{Miller Lab} \ (\href{https://millerlab.faculty.ucdavis.edu}{\small \emph{\underline{\smash{millerlab.faculty.ucdavis.edu})}}} }
			{\textbf{Auditory Neuroscience \& Speech Recognition Lab}} 
		\item
			Independently brought up, prototyped, and developed a real-time solution to cross-reference external audio inputs with an EEG acquisition system by writing C code on a bare-metal embedded system and designing/assembling a single-bit ADC PCB in Altium. Brought latency down from the previous iteration by a factor of 10.
		\item 
			Configured, built, and designed a custom RTOS (embedded Linux distribution) and cross-toolchain using the Yocto Project in a Linux environment, by using shell command line tools, and by understanding the architectural design of the embedded system, alongside the computer architecture of the host system.
		\item
			Designed/read a number of schematics, consulted a number of datasheets for the various IC components used, utilized the GNU debugger for software-level debugging, and used hardware-level debugging tools such as oscilloscopes, logic analyzers, and function generators to debug circuits that interface with the embedded software.
		\item 
			Implemented an external eye-tracking peripheral using TCP/IP communication and a Python to MATLAB library for use in behavioral studies.
\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\header
			{\textbf{Software Engineer - Intern}} 
			{\textbf{June 2018 - August 2018}}
		\header
			{\textbf{General Atomics}}
			{\textbf{EMS - Software and Controls}} 
		\item
			Leveraged object-oriented and algorithm design principles in an agile software development team environment, to convert the code base for an aircraft landing from the high-level OO scripting language of MATLAB to C++, bringing the runtime of the simulation down by a factor of 2. Despite tight time constraints and minimal assistance, I earned the "MVP" award for saving "hundreds of hours in simulation time and greatly reducing control system tuning efforts".
		\item
			Wrote unit-tests in C++ to verify the accuracy of the simulations, using the Catch testing-framework.


\end{itemize}

\vspace{-1.5em}

\subsection*{Projects}
\sectionbreak


\begin{itemize}
	\item[]
		\header
		{
			\textbf{Smart Dog Collar}
			\emph{\smash{Relevant Course Project}} \ \ \ \footnotesize \emph{C \& Verilog}
		}
			{\textbf{Fall 2019 \& Winter 2020}}
		\item 
			Wrote C code on a bare-metal embedded system, with peripheral interfacing using SPI, I2C, I2S, and UART, to track ambient noise, and cycle between different power modes for the SoC and peripherals.
		\item 
			Designed/read schematics, consulted datasheets, designed/assembled multiple PCBs, and debugged circuits using logic analyzers, oscilloscopes, and other hardware-level debugging tools.

\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\header
		{
			\textbf{Operating Systems}
			\emph{\smash{Relevant Course Project}} \ \ \ \footnotesize \emph{C++}
		}
			{\textbf{Spring 2020}}
		\item 
			Wrote C++ code to implement the functionality of a Linux based Operating System, including the implementation of preemptive threading, building a Linux device driver for a FAT16 file system, and writing typical Linux shell command line tools.

\end{itemize}
\hrule
\begin{itemize}
	\item[]
		\header
		{
			\textbf{Mobile Applications (IOS): }
			\href{https://appadvice.com/app/round-bound/1369632746}{\emph{\underline{\smash{Round 'a Bound}}}}, 
			\href{https://appadvice.com/app/tic-tac-emoji/1346934986}{\emph{\underline{\smash{Tic-Tac Emoji}}}} \ \ \ \footnotesize  \emph{Swift}
		}
			{\textbf{Winter 2017 \& Spring 2018}}
		\item 
			Successfully delivered the products through their full life cycle, by utilizing different APIs to detect physics collisions, exhibiting independently made animations and sound, and incorporating an online leaderboard via a real time database. While formerly published, the apps culminated in over 250 downloads.
\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\header
			{	
				\textbf{Web Development: }
				\href{https://aashpointo.github.io/KmapWebsite/}{\emph{\underline{\smash{aashpointo.github.io/KmapWebsite}}}} \ \ \ \footnotesize \emph{HTML/CSS \& JavaScript}
				}
				{\textbf{Winter 2018}}
		\item
			Implemented the Quine-McCluskey algorithm in JavaScript to compute the \emph{Sum of Products} and \emph{Product of Sums} from a set of truth-table inputs, primarily for use in digital logic design.

\end{itemize}

\end{document}

