\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage[usenames, dvipsnames]{color}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{sectsty}
\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor={black},
}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\renewcommand{\baselinestretch}{1.025}

\subsectionfont{\fontsize{11}{15}\selectfont}


\newcommand{\items}[2]
{
	% @ is a column separator 
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} r}
		#1 & #2 \\
	\end{tabular*}
}


\newcommand{\header}[2]
{
	% @ is a column separator 
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} r}
		\hspace{-27pt} #1 & #2 \\
	\end{tabular*}
}

\newcommand{\sectionbreak}
{
	\vspace{-1.2em}
	\rule{\textwidth}{1.7pt}
	\vspace{-1.7em}
}

\newcommand{\twocol}[2]
{
	\begin{tabular*}{\linewidth}{l @{\hspace{108.5pt}} l}
		#1 & #2 \\
	\end{tabular*}
	\vspace{-15pt}

}

\begin{document}

\begin{center}
	{\LARGE \textbf{Aashir Farooqi}}

	\vspace{0.5em}
	\ (949)-226-9612 \textbar 
	\ afarooqi@ucdavis.edu\textbar
	\ \href{https://github.com/AashPointO}{\emph{\underline{\smash{https://github.com/AashPointO}}}}
	\\
\end{center}
\vspace{-20pt}


\subsection*{Education}
\sectionbreak

\begin{itemize}

	\item[] 
		\header
		{\textbf{University of California, Davis}}
		{\textbf{Fall 2016 - Summer 2020}}
	\item[]
		\vspace{-2.5pt}
	\items
		{\textbf{Major:} Computer Engineering, B.S}
		{}
	\items
		{\textbf{GPA:} 3.4}
		{}
	\items
		{\textbf{CS Coursework:} Algorithm Design \& Analysis, Networks, Operating Systems.}
		{}
	\items
		{\textbf{EE Coursework:} Embedded Systems, Digital Systems, Circuits, Signal Processing.}
		{}
		{\vspace{-0.6em}}

\end{itemize}

\vspace{-24.65pt}

\subsection*{Experience}
\sectionbreak

\begin{itemize}
	\item[]
		\header
		{\textbf{Software Engineer - Research Assistant}} 
		{\textbf{April 2018 - June 2020}}
		\header
		{\textbf{Miller Lab} \ (\href{https://millerlab.faculty.ucdavis.edu}{\small \emph{\underline{\smash{millerlab.faculty.ucdavis.edu})}}} }
		{\textbf{Auditory Neuroscience \& Speech Recognition Lab}} 
	\item
		Implemented object-oriented programming/design principles alongside low-overhead data structures in an embedded system, in order to cross-references external audio inputs with an EEG acquisition system. My improvements brought the latency down from the previous iteration a factor of 10.
	\item 
		Taught myself networking principles, such as TCP/IP communication, to communicate with an external eye-tracking system for use in our behavioral studies. 
	\item 
		Designed a database in MATLAB to track participants in behavioral studies.
		

\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\header
		{\textbf{Software Engineer - Intern}} 
		{\textbf{June 2018 - August 2018}}
		\header
		{\textbf{General Atomics}}
		{\textbf{EMS - Software and Controls}} 
	\item
		Leveraged algorithm design and object-oriented programming/design principles as I rewrote the computationally intensive portions of the codebase for an aircraft landing simulation from MATLAB to C++. Despite tight time constraints and minimal assistance, I earned the "MVP" award for saving "hundreds of hours in simulation time and greatly reducing control system tuning efforts".


\end{itemize}

\vspace{-1.5em}

\subsection*{Projects}
\sectionbreak


\begin{itemize}
	\item[]
		\header
		{
			\textbf{Algorithm Design \& Analysis (Course Project): }
		}
		{\textbf{Summer 2020}}
	\item 
		Implemented, tested, and designed a number of different Algorithms in C++, utilizing well-known mathematical optimization methods such as dynamic programming and greedy algorithms. 

\end{itemize}

\hrule

\begin{itemize}
\item[]
	\header
	{
		\textbf{Networking Simulations (Course Project): }
	}
	{\textbf{Spring 2020}}
\item 
	Simulated the behavior of a Wireless Local Area Network and a single server queue in C++ for the sake of modeling and analysis. 
\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\header
		{
			\textbf{Mobile Applications (Independent Projects): }
			\href{https://appadvice.com/app/round-bound/1369632746}{\emph{\underline{\smash{Round 'a Bound}}}}, 
			\href{https://appadvice.com/app/tic-tac-emoji/1346934986}{\emph{\underline{\smash{Tic-Tac Emoji}}}} \ \ \ \footnotesize  \emph{Swift}
		}
		{\textbf{Winter 2017 \& Spring 2018}}
	\item 
		Utilized the Spritekit API to detect physics collisions between nodes and to exhibit independently made animations and sounds.
	\item
		Implemented a realtime database for use in an online leaderboard via Google's Firebase API.
	\item
		Apps originally published and reviewed on the App Store, culminating in over 250 downloads.
\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\header
		{	
			\textbf{Web Applications (Independent Projects): }
			\href{https://aashpointo.github.io/KmapWebsite/}{\emph{\underline{\smash{aashpointo.github.io/KmapWebsite}}}} \ \ \ \footnotesize \emph{HTML/CSS \& JavaScript}
		}
		{\textbf{Winter 2018}}
	\item
		Taught myself how to create Web Applications using JavaScript in order to implement the Quine-McCluskey algorithm from a set of truth-table inputs.

\end{itemize}

\vspace{-1.5em}
\subsection*{Technical Skills}
\sectionbreak

\begin{itemize}

	\item
		\textbf{Proficient:} C/C++, Java, MATLAB, Bash.
	\item
		\textbf{Familiar:} Python, Rust, Swift, R, \LaTeX.
\end{itemize}



\end{document}

