\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage[usenames, dvipsnames]{color}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\hypersetup{
	colorlinks = true,
	urlcolor={black},
}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}
\renewcommand{\baselinestretch}{1.025}

\newcommand{\items}[2]
{
	% @ is a column separator 
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} r}
		#1 & #2 \\
	\end{tabular*}
}


\newcommand{\header}[2]
{
	% @ is a column separator 
	\begin{tabular*}{\linewidth}{l @{\extracolsep{\fill}} r}
		 #1 & #2 \\
	\end{tabular*}
}

\newcommand{\sectionbreak}
{
	\vspace{-1.2em}
	\rule{\textwidth}{1.7pt}
	\vspace{-1.7em}
}

\newcommand{\twocol}[2]
{
	\begin{tabular*}{\linewidth}{l @{\hspace{108.5pt}} l}
		 #1 & #2 \\
	\end{tabular*}
	\vspace{-15pt}

}

\begin{document}

\begin{center}
{\LARGE \textbf{Aashir Farooqi}}

\vspace{0.5em}
\ (949)-226-9612 \textbar 
\ afarooqi@ucdavis.com \textbar
\ \href{https://github.com/AashPointO}{\emph{\underline{\smash{https://github.com/AashPointO}}}}
\\
\end{center}
\vspace{-20pt}


\subsection*{Education}
\sectionbreak

\begin{itemize}

\item[] 
	\header
		{\textbf{University of California, Davis}}
		{\textbf{Fall 2016 - Summer 2020}}
\item[]
	\vspace{-2.5pt}
	\items
		{B.S. Computer Engineering}
		{}
	\items
		{\emph{GPA:} 3.4}
{\vspace{-0.6em}}
	
\end{itemize}

\vspace{-24.65pt}



\subsection*{Technical Skills}
\sectionbreak

\begin{itemize}
	\item[]
		\twocol
		{\textbf{Programming/Markup Languages:}}
		{\hspace{20pt}\hspace{42pt} \textbf{Technological Environments/Libraries:}}
	\item[]
		\begin{tabular*}{\linewidth}{l @{\hspace{152.5pt} \hspace{39pt}} l}
			 C/C++, Rust, Bash, RISC-V,   & SPICE, Linux/UNIX, ModelSim, \\
			 Verilog, HTML/CSS, MATLAB, &  Vim, Android Studio, Quartus,  \\
			 Python, Java, JavaScript, \LaTeX. & Git, EAGLE, Altium.
		\end{tabular*}		
\end{itemize}

\vspace{-1.5em}

\subsection*{Experience}
\sectionbreak



\begin{itemize}
	\item[]
		\items
			{\textbf{Research Assistant}} 
			{\textbf{April 2018 - June 2020}}
		\items
		{\textbf{Miller Lab} \ (\href{https://millerlab.faculty.ucdavis.edu}{\small \emph{\underline{\smash{millerlab.faculty.ucdavis.edu})}}} }
			{\textbf{Auditory Neuroscience and Speech Recognition Lab}} 
		\item
			Independently brought up, prototyped, and implemented a hybrid hardware/embedded system to cross-reference external audio and serial data inputs with our EEG acquisition system in real-time. Brought latency down from the previous iteration by a factor of 10.
		\item
			Wrote embedded firmware code, created hardware schematics, and designed/assembled/debugged multiple PCBs. 
\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\items
			{\textbf{Software Engineering Intern}} 
			{\textbf{June 2018 - August 2018}}
		\items
			{\textbf{General Atomics}}
			{\textbf{EMS - Software and Controls}} 
		\item
			Converted mathematical intensive algorithms of the aircraft landing simulation from MATLAB to C++, bringing the runtime of the simulation down by over a factor of 2. My performance optimization is now used in research and development of the actual aircraft landing system contracted for the world’s most expensive aircraft carriers.
		\item
			Implemented software principle of Test-Driven Development, including custom unit tests to verify my simulation. 
		\item
			Only intern in department of over 20 to earn "MVP" award for saving "hundreds of hours in simulation time, greatly reducing control system tuning efforts".

\end{itemize}

\vspace{-1.5em}

\subsection*{Projects}
\sectionbreak

\begin{itemize}
	\item[]
		\items
			{\textbf{Relevant Course Projects :} \ \ \ \footnotesize  \emph{C/C++, Verilog, RISC-V \& Linux} }
			{\textbf{Fall 2019 - June 2020}}
		\item
			Implemented multiple Linux operating system functionality right outside the kernel, such as preemptive scheduling of different processes and support for multi-threaded safe variables.
		\item 
			Configured an embedded system in C to interact with Amazon Web Services alongside a weather API for automated control of a fan using an IR emitter, and display onto an OLED via SPI.
\end{itemize}

\hrule 

\begin{itemize}
	\item[]
		\items 
		{
			\textbf{Senior Design Project (Embedded Systems): }
			\emph{\smash{Smart Dog Collar}} \ \ \ \footnotesize \emph{C \& Verilog}
		}
			{\textbf{Fall 2019 \& Winter 2020}}
		\item 
			Wrote embedded firmware and HDL code onto Cypress's PSoC. Incorporated a BLE module for wakeup interrupts and data transfer from a mobile application to our device. 
		\item 
			Communicated with external peripherals such as MEMS mics, accelerometers, and gyrometers through I$^{2}$C, I$^{2}$S, and SPI. Included sensors with redundant functionality, to ensure a fault-tolerant product.
		\item 
			Refined skills in hardware debugging through use of multimeters, logic analyzer, and an oscilloscope 
		\item
			Designed multiple iterations of PCBs through Altium, which I assembled through use of soldering irons and hot air stations.

\end{itemize}

\hrule

\begin{itemize}
	\item[]
		\items 
		{
			\textbf{IOS Games (Formerly Published): }
			\href{https://appadvice.com/app/round-bound/1369632746}{\emph{\underline{\smash{Round 'a Bound}}}}, 
			\href{https://appadvice.com/app/tic-tac-emoji/1346934986}{\emph{\underline{\smash{Tic-Tac Emoji}}}} \ \ \ \footnotesize  \emph{Swift}
		}
			{\textbf{Winter 2017 \& Spring 2018}}
		\item 
			Utilized the Spritekit API to detect physics collisions between nodes and display independently made animations and sounds.
		\item
			Incorporated an online leaderboard via a realtime database through Google's Firebase API, which parses through JSON data. 
\end{itemize}

\end{document}

